Validation failed EVT

### 2023-03-30 analysis/article-results.Rmd
Editing readme

knitr::opts_chunk$set(
  echo = FALSE, 
  out.width = "70%", 
  warning = FALSE, 
  message = FALSE,
  fig.retina = 2L
)

@@

```{r dev-calib}
calplot_MI(
  imps_long = imps_all %>% 
    filter(imps_label == "imps_assess" & dataset == "develop"),
  model = validation_dev_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 100,
  xlim = c(0, 0.85),
  ylim = c(-0.25, 1)
) +
  theme_minimal()
```

## External validation

@@

calplot_ext

ggsave(
  calplot_ext,
  filename = "analysis/figures/calibration-plot-ext.png",
  width = 8,
  height = 5,
  units = "in",
  dpi = 300, 
  bg = "white"
)
```

@@

ggsave(
  calplot_combined,
  filename = "analysis/figures/calibration-plot-combined.png",
  width = 8,
  height = 5,
  units = "in",
  dpi = 300, bg = "white"
)
```

@@

```{r nom-export, results='hide'}
png(
  filename = "analysis/figures/nomogram-combined.png",
  width = 8,
  height = 11,
  units = "in",
  res = 300
)
plot(nom)
dev.off()

>>>>

knitr::opts_chunk$set(
  echo = FALSE, 
  out.width = "70%", 
  warning = FALSE, 
  message = FALSE,
  fig.retina = 3L
)

@@

```{r dev-calib}
calplot_MI(
  imps_long = imps_all %>% 
    filter(imps_label == "imps_assess" & dataset == "develop"),
  model = validation_dev_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 100,
  xlim = c(0, 0.85),
  ylim = c(-0.25, 1)
) +
  theme_minimal() + 
  labs(x = "Predicted probability", y = "Observed proportion")
```

## Temporal validation

@@

calplot_ext
```

@@

ggsave(
  calplot_combined,
  filename = "analysis/manuscript-figures/calibration-plot-combined.png",
  width = 8,
  height = 5,
  units = "in",
  dpi = 300, bg = "white"
)
```

@@

```{r nom-export, results='hide'}
png(
  filename = "analysis/manuscript-figures/nomogram-combined.png",
  width = 8,
  height = 11,
  units = "in",
  res = 300
)
plot(nom)
dev.off()
